\Title

### 2020-03-03 manuscript/manuscript.tex
Standardize source bellow data layout name
Replace "beneath" for "bellow" when naming the layout.

The \emph{source beneath data} layout locates one source bellow each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source beneath data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source beneath data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

@@

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source beneath data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/source-layouts-schematics.pdf}
    \caption{
        Source layouts.
        (a) Set of synthetic observation points that resemble a ground survey.
        (b) Location of sources obtained through the \emph{sources beneath
            data} layout.
        (c) Location of sources obtained through the \emph{block averaged
            sources} layout.
        (d) Location of sources obtained through the \emph{grid sources}
            layout.
    }
    \label{fig:source-layouts-schematics}
\end{figure*}

>>>>

The \emph{source bellow data} layout locates one source bellow each
observation point, therefore the number of sources will be equal to the number
of data points.

When working with ground surveys, the \emph{regular grid} needs the grid
spacing to be sufficiently small so observed values can be accurately
reproduced by the source distribution.
This will create too many sources on areas where no observation has been
carried out.
In contrast, the \emph{source bellow data} layout is more likely to accurately
fit the observed data with much less sources, reducing the computational load
to fit the equivalent sources' coefficients.

When working with airborne surveys, the \emph{source bellow data} may
generate an anisotropic distribution of sources by locating too many sources
along the flight paths.
It could lead to unwanted aliases on the predicted values.
In contrast, the \emph{regular grid} won't generate aliases by homogeneously
locating sources.

@@

The number of sources created by this new distribution will be less or equal to
the ones created by the \emph{source bellow data} and the \emph{regular
grid} with the same spacing.
Moreover, the sources are only located beneath populated blocks, so sources
will be concentrated on regions where data has been gathered and no anisotropic
distribution of sources will be generated.

@@
